Kernel k-Groups via Hartigan's Method

### 2018-08-10 energy_clustering/pami18/energy_clustering.tex
pami update

\begin{figure*}
\centering
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{gauss_1d.pdf}\\[-2em]
(a)
\end{minipage}
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{loggauss_1d.pdf} \\[-2em]
(b)
\end{minipage}\\[1em]
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{normal_density.pdf}\\[-2em]
(c)
\end{minipage}\hspace{2em}
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{lognormal_density.pdf}\\[-2em]
(d)
\end{minipage}
\caption{
\label{fig:1dexperiment}
Clustering one-dimensional data for a two-class problem.
(a) $x \stackrel{iid}{\sim} \tfrac{1}{2} \mathcal{N}(0, 1.5) +
\tfrac{1}{2}\mathcal{N}(1.5,0.3)$. (b) $x \stackrel{iid}{\sim}
\tfrac{1}{2}e^{\mathcal{N}(0, 1.5)} + \tfrac{1}{2} e^{\mathcal{N}(1.5, 0.3)}$.
In both cases we plot the accuracy versus the total number of points.
(c) Kernel density estimation for a single trial with 2000 sampled
points from the
distribution in the case (a). (d) Kernel density estimation in a single
trial with 
2000 points sampled from the distribution in the case (b).
}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.33\textwidth]{gauss1.pdf}
\includegraphics[width=0.33\textwidth]{gauss2.pdf}
\includegraphics[width=0.33\textwidth]{gauss_n.pdf}
\includegraphics[width=0.33\textwidth]{loggauss_n.pdf}
\includegraphics[width=0.315\textwidth]{gauss_unbal.pdf}
\put(-400,130){(a)}
\put(-230,130){(b)}
\put(-50,130){(c)}
\put(-320,-8){(d)}
\put(-140,-8){(e)}
\caption{
\label{fig:plots}
Clustering results associated to the data illustrated in 
Fig.~\ref{fig:scatter}. For each experiment we
perform 100 Monte Carlo runs. Error bars indicate standard error.
(a)
High dimensional Gaussian mixture according to \eqref{eq:gauss1}.
The dashed line is
Bayes accuracy $\approx 0.86$. We use the metric $\rho_1$ in
\eqref{eq:rho_alpha}, which is standard in energy statistics.
(b)
High dimensional Gaussian mixture according to \eqref{eq:gauss2}.
Bayes accuracy $\approx 0.95$. We use $\rho_1$ in \eqref{eq:rho_alpha}.
(c)
Gaussian mixture with parameters \eqref{eq:20gauss}. We increase
the number of sampled points in each trial. We use different
metrics; see \eqref{eq:rho_alpha}--\eqref{eq:rho_hat}. 
Here, kernel k-groups is more accurate than spectral clustering.
(d)
Same experiment as in Fig.~\ref{fig:plots}c but with a 
lognormal mixture with parameters \eqref{eq:20gauss}.
Again, kernel k-groups is more accurate than alternatives.
The plot suggests that neither of these methods are
consistent on this example since Bayes accuracy is $\approx 0.90$.
(e)
Comparison between clustering methods
on unbalanced clusters. The data is normally 
distributed as \eqref{eq:gauss3} where
we vary $m \in [0, 240]$. We use the standard metric $\rho_1$ (see
\eqref{eq:rho_alpha}) from energy statistics.
}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=.24\textwidth]{2cigars.pdf}
\includegraphics[width=.24\textwidth]{2circles.pdf}
\put(-240,-8){(a)}
\put(-110,-8){(b)}
\caption{
\label{fig:2dscatter}
(a) Data distributed as 
$x \stackrel{iid}{\sim}
\tfrac{1}{2}\mathcal{N}(\mu_1,\Sigma_1)+
\tfrac{1}{2}\mathcal{N}(\mu_1,\Sigma_1)$, 
$\mu_1= (0,0)^\top$, 
$\mu_2 = (6.5, 0)^\top$ and 
$\Sigma_1 = \Sigma_2 = \diag(1, 20)$. We sample $800$ points.
(b) Concentric circles with radius $r_1 = 1$ and $r_2 = 3$, with 
noise $0.2 \cdot \mathcal{N}(0, I_2)$. We sample 
800 points with probability $1/2$ for each class.
} 
\end{figure}

@@

\begin{IEEEbiography}{Guilherme Fran\c ca}
Biography text here.
\end{IEEEbiography}

@@

\begin{IEEEbiographynophoto}{Joshua T.~Vogelstein}
I received a B.S degree from the Department of Biomedical Engineering (BME) at Washington University in St. Louis, MO in 2002, a M.S. degree from the Department of Applied Mathematics and Statistics (AMS) at Johns Hopkins University (JHU) in Baltimore, MD in 2009, and a Ph.D. degree from the Department of Neuroscience at JHU in 2009. I was a Postdoctoral Fellow in AMS@JHU from 2009 until 2011, at which time I was appointed an Assistant Research Scientist, and became a member of the Institute for Data Intensive Science and Engineering. I spent 2 years at Information Initiative at Duke University, before coming home to my current appointment as Assistant Professor in BME@JHU, and core faculty in both the Institute for Computational Medicine and the Center for Imaging Science, as well as a member of the Kavli Neuroscience Discovery Institute. I married my kindergarten sweetheart in the summer of 2014.

My primary research interest is to extend and fuse statistical machine learning and big data science to address the most important brain science and mental health questions of our time, particularly  connectomics. Our group’s research has been featured in a number of prominent scientific and engineering journals and conferences including Nature, Nature Methods, Science, Cell, PNAS, Science Translational Medicine, JMLR, PAMI, Annals of Applied Statistics,  NIPS, and SIAM Journal of Matrix Analysis and Applications. In 2011, I co-founded the Open Connectome Project which expanded in 2015 to be NeuroData, whose mission is to enable terascale neuroscience for everyone. All our work is conducted according to the highest standards of open science.
\end{IEEEbiographynophoto}

>>>>

\begin{figure*}
\centering
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{gauss_1d.pdf}\\[-2em]
(a)
\end{minipage}
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{loggauss_1d.pdf} \\[-2em]
(b)
\end{minipage}\\[1em]
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{normal_density.pdf}\\[-2em]
(c)
\end{minipage}\hspace{2em}
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{lognormal_density.pdf}\\[-2em]
(d)
\end{minipage}
\caption{
\label{fig:1dexperiment}
Clustering one-dimensional data for a two-class problem.
(a) $x \stackrel{iid}{\sim} \tfrac{1}{2} \mathcal{N}(0, 1.5) +
\tfrac{1}{2}\mathcal{N}(1.5,0.3)$. (b) $x \stackrel{iid}{\sim}
\tfrac{1}{2}e^{\mathcal{N}(0, 1.5)} + \tfrac{1}{2} e^{\mathcal{N}(1.5, 0.3)}$.
In both cases we plot the average accuracy versus the total number of points.
We ommit error bars since they are too small.
(c) Kernel density estimation for a single trial with 2000 sampled
points from the
distribution in the case (a). (d) Kernel density estimation in a single
trial with 
2000 points sampled from the distribution in the case (b).
}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.33\textwidth]{gauss1.pdf}
\includegraphics[width=0.33\textwidth]{gauss2.pdf}
\includegraphics[width=0.33\textwidth]{gauss_n.pdf}
\includegraphics[width=0.33\textwidth]{loggauss_n.pdf}
\includegraphics[width=0.315\textwidth]{gauss_unbal.pdf}
\put(-400,130){(a)}
\put(-230,130){(b)}
\put(-50,130){(c)}
\put(-320,-8){(d)}
\put(-140,-8){(e)}
\caption{
\label{fig:plots}
Clustering results associated to the data illustrated in 
Fig.~\ref{fig:scatter}. For each experiment we
perform 100 Monte Carlo runs and show the average accuracy. 
We ommit error bars since they are too small to be visible.
(a)
High dimensional Gaussian mixture according to \eqref{eq:gauss1}.
The dashed line is
Bayes accuracy $\approx 0.86$. We use the metric $\rho_1$ in
\eqref{eq:rho_alpha}, which is standard in energy statistics.
(b)
High dimensional Gaussian mixture according to \eqref{eq:gauss2}.
Bayes accuracy $\approx 0.95$. We use $\rho_1$ in \eqref{eq:rho_alpha}.
(c)
Gaussian mixture with parameters \eqref{eq:20gauss}. We increase
the number of sampled points in each trial. We use different
metrics; see \eqref{eq:rho_alpha}--\eqref{eq:rho_hat}. 
Here, kernel k-groups is more accurate than spectral clustering.
(d)
Same experiment as in Fig.~\ref{fig:plots}c but with a 
lognormal mixture with parameters \eqref{eq:20gauss}.
Again, kernel k-groups is more accurate than alternatives.
The plot suggests that neither of these methods are
consistent on this example since Bayes accuracy is $\approx 0.90$.
(e)
Comparison between clustering methods
on unbalanced clusters. The data is normally 
distributed as \eqref{eq:gauss3} where
we vary $m \in [0, 240]$. We use the standard metric $\rho_1$ (see
\eqref{eq:rho_alpha}) from energy statistics.
}
\end{figure*}

@@

\begin{figure}
\centering
\begin{minipage}{0.2\textwidth}
\includegraphics[width=1\textwidth]{2cigars.pdf}\\[-.2em](a)
\end{minipage}\hspace{2em}
\begin{minipage}{0.2\textwidth}
\includegraphics[width=1\textwidth]{2circles.pdf}\\[-.2em](b)
\end{minipage}
\caption{
\label{fig:2dscatter}
(a) Data distributed as 
$x \stackrel{iid}{\sim}
\tfrac{1}{2}\mathcal{N}(\mu_1,\Sigma_1)+
\tfrac{1}{2}\mathcal{N}(\mu_1,\Sigma_1)$, 
$\mu_1= (0,0)^\top$, 
$\mu_2 = (6.5, 0)^\top$ and 
$\Sigma_1 = \Sigma_2 = \diag(1, 20)$. We sample $800$ points.
(b) Concentric circles with radius $r_1 = 1$ and $r_2 = 3$, with 
noise $0.2 \cdot \mathcal{N}(0, I_2)$. We sample 
800 points with probability $1/2$ for each class.
} 
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{gui2.png}}]{Guilherme Fran\c ca} 
has a BSc in physics, and received both his MSc and 
PhD in Theoretical Physics from the Institute of 
Theoretical Physics IFT-UNESP/ICTP-SAIFR (2012). He was a Postdoctoral Fellow
with the High Energy Theory group in the Physics Department 
at Cornell University (2013--2015), working on topics of mathematical physics
and non-perturbative methods in quantum field theory 
and statistical mechanics.
He was a Postdoctoral Fellow in
the Computer Science Department at Boston College (2015), working in
optimization theory.
Since 2016 he is a Postdoctoral Fellow at Johns Hopkins University, currently
with the Mathematical Institute for Data Science (MINDS). 
His current research interests are in theoretical methods in the broad
area of machine learning 
and optimization.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{jovo.png}}]{Joshua~T.~Vogelstein}
I received a B.S degree from the Department of Biomedical Engineering (BME) at Washington University in St. Louis, MO in 2002, a M.S. degree from the Department of Applied Mathematics and Statistics (AMS) at Johns Hopkins University (JHU) in Baltimore, MD in 2009, and a Ph.D. degree from the Department of Neuroscience at JHU in 2009. I was a Postdoctoral Fellow in AMS@JHU from 2009 until 2011, at which time I was appointed an Assistant Research Scientist, and became a member of the Institute for Data Intensive Science and Engineering. I spent 2 years at Information Initiative at Duke University, before coming home to my current appointment as Assistant Professor in BME@JHU, and core faculty in both the Institute for Computational Medicine and the Center for Imaging Science, as well as a member of the Kavli Neuroscience Discovery Institute. I married my kindergarten sweetheart in the summer of 2014.

My primary research interest is to extend and fuse statistical machine learning and big data science to address the most important brain science and mental health questions of our time, particularly  connectomics. Our group’s research has been featured in a number of prominent scientific and engineering journals and conferences including Nature, Nature Methods, Science, Cell, PNAS, Science Translational Medicine, JMLR, PAMI, Annals of Applied Statistics,  NIPS, and SIAM Journal of Matrix Analysis and Applications. In 2011, I co-founded the Open Connectome Project which expanded in 2015 to be NeuroData, whose mission is to enable terascale neuroscience for everyone. All our work is conducted according to the highest standards of open science.
\end{IEEEbiography}
